\bf Title here

### 2020-07-30 paper/paper.Rmd
another read-through

The optimisation problem we're interested in is in the context of projection pursuit guided tour. Coined by @friedman1974projection, projection pursuit detects interesting structures (i.e. clustering, outliers and skewness) in multivariate data via projecting it in lower dimensions. Let $\mathbf{X}_{n \times p}$ be the data matrix, an n-d projection can be seen as a linear transformation $T: \mathbb{R}^p \mapsto \mathbb{R}^d$ defined by $\mathbf{P} = \mathbf{X} \cdot \mathbf{A}$, where $\mathbf{P}_{n \times d}$ is the projected data and $\mathbf{A}_{p\times d}$ is the projection basis. Define $f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}$ be an index function that maps the projection basis $\mathbf{A}$ onto a scalar index value $I$, this function is commonly known as the projection pursuit index (PPI) function, or the index function and is used to measure the "interestingness" of the projection. A number of index functions have been proposed in the literature to detect different data structures, including Legendre index [@friedman1974projection], Hermite index [@hall1989polynomial], natural Hermite index [@cook1993projection], chi-square index [@posse1995projection], LDA index [@lee2005projection] and PDA index [@lee2010projection].

In their initial paper, @friedman1974projection noted that "..., the technique use for maximising the projection index strongly influences both the statistical and the computational aspects of the procedure." Hence, effective optimisation algorithms are necessary for projection pursuit to find bases that give interesting projections. While we leave the formal construction the optimisation problem and existing algorithms in section \ref{tour-optim}, we want to emphasizes here that given a random starting (current) basis, projection pursuit repetitively searches for candidate bases nearby and outputs a target basis once it finds one with higher index value than the current basis. The target basis becomes the current basis in the next iteration and the searching continues until no better basis can be found or the termination criteria are reached.

A tour method, guided tour is usually used in conjunction with projection pursuit to interactively explore multivariate data. Tour plays an animation on the projected data which is constructed using the bases outputted by projection pursuit and their interpolations. Guided tour constructs the interpolation using the shortest geodesic path between two outputted bases and we refer readers to @buja2005computational for details of the mathematical construction of the interpolation basis  Figure \ref{tour-path} shows a sketch of the tour path consisting of the blue frames produced by projection pursuit and the white frames, which interpolates two blue frames. The tour method has been implemented in the *tourr* package in R, available on the Comprehensive R Archive Network at [https://cran.r-project.org/web/packages/tourr/](https://cran.r-project.org/web/packages/tourr/) [@wickham2011tourrpackage].

@@

We can see from Figure \ref{tour-path} that only the data projected using the outputted bases and interpolated bases are animated by tour; none of the searching bases are presented in the tour animation. The optimisation algorithms in projection pursuit, although has been demonstrated to find the global maximum in various literature we referred above, focuses solely on finding the global maximum and remains as black-box mechanisms There has been fewer tools available to explore how each algorithm iteratively finds its maximum and compare how different algorithms searches the parameter space. Visualisation has been widely used for exploring and understanding data. Presenting information in a graphical manner often allows people to see information they would otherwise not seen. This motivates us **to develop a visual framework to diagnose optimisation algorithms in projection pursuit with a aim to understand and compare different existing algorithms.** This study is meaningful because **as more complex index functions are proposed, only an appropriate optimisation algorithm allows us to find the projection basis that presents interesting underlying structure in the data**.

The idea of generalised framework for diagnostic plots is inspired by the concept of grammar of graphic [@wickham2010layered], which powers the primary graphical system in R, ggplot2 [@ggplot2]. In grammar of graphic, plots are not defined by its appearance (i.e. boxplot, histogram, scatter plot etc) but by "stacked layers". Using this design, ggplot doesn't have to develop a gazillion of functions that each produces a different type of plot from a different data structure. Instead, it aesthetically maps variables (and its statistical transformation) in a dataset to different geometric objects (points, lines, box-and-whisker etc) and builds the plot through overlaying different layers. There are different ways to represent the same data in rectangular form. Certain cleaning steps are needed, before using ggplot2, to bring the data into a tidy data format [@wickham2014tidy] where 1) each observation forms a row; 2) each variable forms a column and 3) each type of observational unit forms a table. In a tidy format, data wrangling and visualisation are greatly simplified.

@@

 For our visual diagnostics, global object is a such data construction with key components in optimisation algorithms and is designed for making diagnostic plots easier. In the optimisation algorithms for projection pursuit, two key elements are the projection basis: $\mathbf{A}$ and the index value: $I$. State: $S$ labels the observation with detailed stage of searching or interpolation.

Multiple iterators are needed to index the data collected at different levels. $t$ is a unique identifier that prescribes the natural ordering of each observation; $j$ is the counter for each search-and-interpolate round, which remains the same for within one round and has an increment of one once a new round starts. $l$ is the counter for each search/interpolation allowing us to know how many basis has the algorithm searched before finding one to output.

@@

There are other parameters that are of our interest and we denote them as *$V_{p}$*. In projection pursuit, this includes $V_1 = \text{method}$, which tags the name of the algorithm used and $V_2 = \text{alpha}$, which is the neighbourhood parameter that controls the size in sampling candidate bases. The data structure can thus be shown as in Equation \ref{eq:data-structure}.

>>>>

Coined by @friedman1974projection, projection pursuit detects interesting structures (i.e. clustering, outliers and skewness) in multivariate data via projecting onto lower dimensions. Let $\mathbf{X}_{n \times p}$ be the data matrix, an n-d projection can be seen as a linear transformation $T: \mathbb{R}^p \mapsto \mathbb{R}^d$ defined by $\mathbf{P} = \mathbf{X} \cdot \mathbf{A}$, where $\mathbf{P}_{n \times d}$ is the projected data and $\mathbf{A}_{p\times d}$ is the projection basis. Define $f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}$ be an index function that maps the projection basis $\mathbf{A}$ onto an index value $I$, this function is commonly known as the projection pursuit index (PPI) function, or the index function and is used to measure the "interestingness" of a projection. A number of index functions have been proposed in the literature to detect different data structures, including Legendre index [@friedman1974projection], Hermite index [@hall1989polynomial], natural Hermite index [@cook1993projection], chi-square index [@posse1995projection], LDA index [@lee2005projection] and PDA index [@lee2010projection].

In their initial paper, @friedman1974projection noted that "..., the technique use for maximising the projection index strongly influences both the statistical and the computational aspects of the procedure." Hence, effective optimisation algorithms are necessary for projection pursuit to find the bases that give interesting projections. While we leave the formal construction of the optimisation problem and existing algorithms in section \ref{tour-optim}, we outlines the general idea here. Given a random starting (current) basis, projection pursuit repetitively searches for candidate bases nearby until it finds one with higher index value than the current basis. In the second round, that basis becomes the current basis and the repetitive sampling  continues. The process ends until no better basis can be found or one of the termination criteria is reached.

A tour method, guided tour is usually used in conjunction with projection pursuit to interactively explore multivariate data. Tour plays an animation on the projected data which is constructed using the bases outputted by projection pursuit and their interpolations. Guided tour constructs the interpolation using the shortest geodesic path between two outputted bases and we refer readers to @buja2005computational for the mathematical details. Figure \ref{tour-path} shows a sketch of the tour path consisting of the blue frames produced by the projection pursuit optimisation algorithm and the white frames, which are the interpolations between two blue frames. The tour method has been implemented in the *tourr* package in R, available on the Comprehensive R Archive Network at [https://cran.r-project.org/web/packages/tourr/](https://cran.r-project.org/web/packages/tourr/) [@wickham2011tourrpackage].

@@

We can see from Figure \ref{tour-path} that only the data projected using the outputted and interpolated bases are animated by tour; none of the searching bases sampled by the optimsiation algorithms are presented in the tour animation. Although these algorithms have been demonstrated to find the global maximum in various literature as we cited above, they focus solely on finding the global maximum and fewer tools are available to explore how each algorithm searches the parameter space and compare the results between different algorithms.

Visualisation has been widely used in exploratory data analysis. Presenting information in a graphical format often allows people to see information they would otherwise not seen. This motivates us **to develop a visual framework to diagnose optimisation algorithms in projection pursuit with a aim to understand and compare different existing algorithms.** This study is meaningful because **as more complex index functions are proposed based on statistical theory, only computationally effective optimisation algorithms allow us to find the projection basis that presents interesting structure in the data**.

The idea of generalised framework for diagnostic plots is inspired by the concept of grammar of graphic [@wickham2010layered], which powers the primary graphical system in R, ggplot2 [@ggplot2]. In grammar of graphic, plots are not defined by its appearance (i.e. boxplot, histogram, scatter plot etc) but by "stacked layers". Using this design, ggplot doesn't have to develop a gazillion of functions that each produces a different type of plot from a different data structure. Instead, it aesthetically maps variables (and its statistical transformation) in a dataset to different geometric objects (points, lines, box-and-whisker etc) and builds the plot through overlaying different layers.

There are different ways to represent the same data in rectangular form. Certain cleaning steps are needed, before using ggplot2, to bring the data into a tidy data format [@wickham2014tidy] where 1) each observation forms a row; 2) each variable forms a column and 3) each type of observational unit forms a table. In a tidy format, data wrangling and visualisation are greatly simplified.

@@

Global object is a data construction with key components from optimisation algorithms and is designed for making diagnostic plots easier. In the optimisation algorithms for projection pursuit, three key elements are 1) projection bases: $\mathbf{A}$, 2) index values: $I$ and 3) State: $S$, which labels the observation with detailed stage of searching or interpolation.

Multiple iterators are needed to index the data collected at different levels. $t$ is a unique identifier that prescribes the natural ordering of each observation; $j$ is the counter for each search-and-interpolate round, which remains the same within one round and has an increment of one once a new round starts. $l$ is the counter for each search/interpolation allowing us to know how many basis the algorithm has searched before finding one to output.

@@

There are other parameters that are of our interest and we denote them as *$V_{p}$*. In projection pursuit, this includes $V_1 = \text{method}$, which tags the name of the algorithm used and $V_2 = \text{alpha}$, the neighbourhood parameter that controls the size in sampling candidate bases. The data structure can thus be shown as in Equation \ref{eq:data-structure}.

### 2020-07-30 paper/paper.tex
another read-through

The optimisation problem we're interested in is in the context of
projection pursuit guided tour. Coined by
\citet{friedman1974projection}, projection pursuit detects interesting
structures (i.e.~clustering, outliers and skewness) in multivariate data
via projecting it in lower dimensions. Let \(\mathbf{X}_{n \times p}\)
be the data matrix, an n-d projection can be seen as a linear
transformation \(T: \mathbb{R}^p \mapsto \mathbb{R}^d\) defined by
\(\mathbf{P} = \mathbf{X} \cdot \mathbf{A}\), where
\(\mathbf{P}_{n \times d}\) is the projected data and
\(\mathbf{A}_{p\times d}\) is the projection basis. Define
\(f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}\) be an index function
that maps the projection basis \(\mathbf{A}\) onto a scalar index value
\(I\), this function is commonly known as the projection pursuit index
(PPI) function, or the index function and is used to measure the
``interestingness'' of the projection. A number of index functions have
been proposed in the literature to detect different data structures,
including Legendre index \citep{friedman1974projection}, Hermite index
\citep{hall1989polynomial}, natural Hermite index
\citep{cook1993projection}, chi-square index
\citep{posse1995projection}, LDA index \citep{lee2005projection} and PDA
index \citep{lee2010projection}.

In their initial paper, \citet{friedman1974projection} noted that
``\ldots{}, the technique use for maximising the projection index
strongly influences both the statistical and the computational aspects
of the procedure.'' Hence, effective optimisation algorithms are
necessary for projection pursuit to find bases that give interesting
projections. While we leave the formal construction the optimisation
problem and existing algorithms in section \ref{tour-optim}, we want to
emphasizes here that given a random starting (current) basis, projection
pursuit repetitively searches for candidate bases nearby and outputs a
target basis once it finds one with higher index value than the current
basis. The target basis becomes the current basis in the next iteration
and the searching continues until no better basis can be found or the
termination criteria are reached.

A tour method, guided tour is usually used in conjunction with
projection pursuit to interactively explore multivariate data. Tour
plays an animation on the projected data which is constructed using the
bases outputted by projection pursuit and their interpolations. Guided
tour constructs the interpolation using the shortest geodesic path
between two outputted bases and we refer readers to
\citet{buja2005computational} for details of the mathematical
construction of the interpolation basis Figure \ref{tour-path} shows a
sketch of the tour path consisting of the blue frames produced by
projection pursuit and the white frames, which interpolates two blue
frames. The tour method has been implemented in the \emph{tourr} package
in R, available on the Comprehensive R Archive Network at
\url{https://cran.r-project.org/web/packages/tourr/}
\citep{wickham2011tourrpackage}.

@@

We can see from Figure \ref{tour-path} that only the data projected
using the outputted bases and interpolated bases are animated by tour;
none of the searching bases are presented in teh tour animation. The
optimisation algorithms in projection pursuit, although has been
demonstrated to find the global maximum in various literature we
referred above, focuses solely on finding the global maximum and remains
as black-box machanisms. There has been fewer tools available to explore
how each algorithm iteratively finds its maximum and compare how
different algorithms searches the parameter space. Visualisation has
been widely used for exploring and understanding data. Presenting
information in a graphical manner often allows people to see information
they would otherwise not seen. This motivates us \textbf{to develop a
visual framework to diagnose optimisation algorithms in projection
pursuit with a aim to understand and compare different existing
algorithms.} This study is meaningful because \textbf{as more complex
index functions are proposed, only an appropriate optimisation algorithm
allows us to find the projection basis that presents interesting
underlying structure in the data}.

The idea of generalised framwork for diagnostic plots is inspired by the
concept of grammar of graphic \citep{wickham2010layered}, which powers
the primary graphical system in R, ggplot2 \citep{ggplot2}. In grammar
of graphic, plots are not defined by its appearance (i.e.~boxplot,
histogram, scatter plot etc) but by ``stacked layers''. Using this
design, ggplot doesn't have to develop a gazillion of functions that
each produces a different type of plot from a different data structure.
Instead, it aesthetically maps variables (and its statistical
transformation) in a dataset to different geometric objects (points,
lines, box-and-whisker etc) and builds the plot through overlaying
different layers. There are different ways to represent the same data in
rectangular form. Certain cleaning steps are needed, before using
ggplot2, to bring the data into a tidy data format
\citep{wickham2014tidy} where 1) each observation forms a row; 2) each
variable forms a column and 3) each type of observational unit forms a
table. In a tidy format, data wrangling and visualisation are greatly
simplified.

@@

For our visual diagnostics, global object is a such data construction
with key components in optimisation algorithms and is designed for
making diagnostic plots easier. In the optimisation algorithms for
projection pursuit, two key elements are the projection basis:
\(\mathbf{A}\) and the index value: \(I\). State: \(S\) labels the
observation with detailed stage of searching or interpolation.

Multiple iterators are needed to index the data collected at different
levels. \(t\) is a unique identifier that prescribes the natural
ordering of each observation; \(j\) is the counter for each
search-and-interpolate round, which remains the same for within one
round and has an increment of one once a new round starts. \(l\) is the
counter for each search/interpolation allowing us to know how many basis
has the algorithm searched before finding one to output.

There are other parameters that are of our interest and we denote them
as \emph{\(V_{p}\)}. In projection pursuit, this includes
\(V_1 = \text{method}\), which tags the name of the algorithm used and
\(V_2 = \text{alpha}\), which is the neighbourhood parameter that
controls the size in sampling candidate bases. The data structure can
thus be shown as in Equation \ref{eq:data-structure}.

\begin{equation}
\left[
\begin{array}{c|ccc|cc|cc}
t & \mathbf{A} & I & S & j &  l  & V_{1} & V_{2}\\
\hline
1 & \mathbf{A}_1 & I_1 & S_1 & 1 & 1 & V_{11} & V_{21}\\
\hline
2 & \mathbf{A}_2 & I_2 & S_2 & 2 & 1  & V_{12}  & V_{22}\\
3 & \mathbf{A}_3 & I_3 & S_3 & 2 & 2  & V_{13}  & V_{23}\\
\vdots & \vdots &\vdots &\vdots  &\vdots & \vdots &\vdots  &\vdots\\
\vdots & \vdots & \vdots &\vdots & 2 & l_2 & \vdots  & \vdots\\
\hline
\vdots &\vdots & \vdots &\vdots & 2  & 1& \vdots & \vdots\\
\vdots &\vdots &\vdots &\vdots & 2 & 2& \vdots &  \vdots\\
\vdots &\vdots &\vdots &\vdots &\vdots & \vdots & \vdots  &\vdots \\
\vdots &\vdots &\vdots &\vdots & 2 & k_2 &\vdots  & \vdots\\
\hline
\vdots &\vdots &\vdots &\vdots &\vdots & \vdots &\vdots &\vdots \\
\hline
\vdots & \vdots & \vdots &\vdots  & J &  1 & \vdots & \vdots \\
\vdots &\vdots &\vdots &\vdots &\vdots & \vdots &\vdots &\vdots \\
T & \mathbf{A}_T & I_T &S_T  & J &  l_{J} & V_{1T}& V_{2T}\\
\hline
\vdots &\vdots & \vdots &\vdots & J  & 1& \vdots & \vdots\\
\vdots &\vdots &\vdots &\vdots &\vdots & \vdots & \vdots  &\vdots \\
\vdots &\vdots &\vdots &\vdots & J & k_J &\vdots  & \vdots\\
\hline
\vdots& \vdots & \vdots & \vdots & J+1 & 1 & \vdots& \vdots\\
\vdots &\vdots &\vdots &\vdots &\vdots & \vdots &\vdots &\vdots \\
T^\prime & \mathbf{A}_{T^\prime} & I_{T^\prime} &S_{T^\prime}  & J+1 &  l_{J+1} & V_{1T^\prime}& V_{2T^\prime}\\
\end{array}
\right]
= 
\left[
\begin{array}{c}
\text{column name} \\
\hline
\text{search (start basis)} \\
\hline
\text{search} \\
\text{search} \\
\vdots \\
\text{search (outputed basis)} \\
\hline
\text{interpolate} \\
\text{interpolate} \\
\vdots \\
\text{interpolate} \\
\hline
\vdots \\
\hline
\text{search} \\
\vdots \\
\text{search (final basis)} \\
\hline
\text{interpolate} \\
\vdots \\
\text{interpolate} \\
\hline
\text{search (no output)} \\
\vdots \\
\text{search (no output)} \\
\end{array}
\right]
\label{eq:data-structure}
\end{equation}

>>>>

Coined by \citet{friedman1974projection}, projection pursuit detects
interesting structures (i.e.~clustering, outliers and skewness) in
multivariate data via projecting onto lower dimensions. Let
\(\mathbf{X}_{n \times p}\) be the data matrix, an n-d projection can be
seen as a linear transformation \(T: \mathbb{R}^p \mapsto \mathbb{R}^d\)
defined by \(\mathbf{P} = \mathbf{X} \cdot \mathbf{A}\), where
\(\mathbf{P}_{n \times d}\) is the projected data and
\(\mathbf{A}_{p\times d}\) is the projection basis. Define
\(f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}\) be an index function
that maps the projection basis \(\mathbf{A}\) onto an index value \(I\),
this function is commonly known as the projection pursuit index (PPI)
function, or the index function and is used to measure the
``interestingness'' of a projection. A number of index functions have
been proposed in the literature to detect different data structures,
including Legendre index \citep{friedman1974projection}, Hermite index
\citep{hall1989polynomial}, natural Hermite index
\citep{cook1993projection}, chi-square index
\citep{posse1995projection}, LDA index \citep{lee2005projection} and PDA
index \citep{lee2010projection}.

In their initial paper, \citet{friedman1974projection} noted that
``\ldots{}, the technique use for maximising the projection index
strongly influences both the statistical and the computational aspects
of the procedure.'' Hence, effective optimisation algorithms are
necessary for projection pursuit to find the bases that give interesting
projections. While we leave the formal construction of the optimisation
problem and existing algorithms in section \ref{tour-optim}, we outlines
the general idea here. Given a random starting (current) basis,
projection pursuit repetitively searches for candidate bases nearby
until it finds one with higher index value than the current basis. In
the second round, that basis becomes the current basis and the
repetitive sampling continues. The process ends until no better basis
can be found or one of the termination criteria is reached.

A tour method, guided tour is usually used in conjunction with
projection pursuit to interactively explore multivariate data. Tour
plays an animation on the projected data which is constructed using the
bases outputted by projection pursuit and their interpolations. Guided
tour constructs the interpolation using the shortest geodesic path
between two outputted bases and we refer readers to
\citet{buja2005computational} for the mathematical details. Figure
\ref{tour-path} shows a sketch of the tour path consisting of the blue
frames produced by the projection pursuit optimisation algorithm and the
white frames, which are the interpolations between two blue frames. The
tour method has been implemented in the \emph{tourr} package in R,
available on the Comprehensive R Archive Network at
\url{https://cran.r-project.org/web/packages/tourr/}
\citep{wickham2011tourrpackage}.

@@

We can see from Figure \ref{tour-path} that only the data projected
using the outputted and interpolated bases are animated by tour; none of
the searching bases sampled by the optimsiation algorithms are presented
in the tour animation. Although these algorithms have been demonstrated
to find the global maximum in various literature as we cited above, they
focus solely on finding the global maximum and fewer tools are available
to explore how each algorithm searches the parameter space and compare
the results between different algorithms.

Visualisation has been widely used in exploratory data analysis.
Presenting information in a graphical format often allows people to see
information they would otherwise not seen. This motivates us \textbf{to
develop a visual framework to diagnose optimisation algorithms in
projection pursuit with a aim to understand and compare different
existing algorithms.} This study is meaningful because \textbf{as more
complex index functions are proposed based on statistical theory, only
computationally effective optimisation algorithms allow us to find the
projection basis that presents interesting structure in the data}.

The idea of generalised framework for diagnostic plots is inspired by
the concept of grammar of graphic \citep{wickham2010layered}, which
powers the primary graphical system in R, ggplot2 \citep{ggplot2}. In
grammar of graphic, plots are not defined by its appearance
(i.e.~boxplot, histogram, scatter plot etc) but by ``stacked layers''.
Using this design, ggplot doesn't have to develop a gazillion of
functions that each produces a different type of plot from a different
data structure. Instead, it aesthetically maps variables (and its
statistical transformation) in a dataset to different geometric objects
(points, lines, box-and-whisker etc) and builds the plot through
overlaying different layers.

There are different ways to represent the same data in rectangular form.
Certain cleaning steps are needed, before using ggplot2, to bring the
data into a tidy data format \citep{wickham2014tidy} where 1) each
observation forms a row; 2) each variable forms a column and 3) each
type of observational unit forms a table. In a tidy format, data
wrangling and visualisation are greatly simplified.

@@

Global object is a data construction with key components from
optimisation algorithms and is designed for making diagnostic plots
easier. In the optimisation algorithms for projection pursuit, three key
elements are 1) projection bases: \(\mathbf{A}\), 2) index values: \(I\)
and 3) State: \(S\), which labels the observation with detailed stage of
searching or interpolation.

Multiple iterators are needed to index the data collected at different
levels. \(t\) is a unique identifier that prescribes the natural
ordering of each observation; \(j\) is the counter for each
search-and-interpolate round, which remains the same within one round
and has an increment of one once a new round starts. \(l\) is the
counter for each search/interpolation allowing us to know how many basis
the algorithm has searched before finding one to output.

There are other parameters that are of our interest and we denote them
as \emph{\(V_{p}\)}. In projection pursuit, this includes
\(V_1 = \text{method}\), which tags the name of the algorithm used and
\(V_2 = \text{alpha}\), the neighbourhood parameter that controls the
size in sampling candidate bases. The data structure can thus be shown
as in Equation \ref{eq:data-structure}.

\begin{equation}
\left[
\begin{array}{c|ccc|cc|cc}
t & \mathbf{A} & I & S & j &  l  & V_{1} & V_{2}\\
\hline
1 & \mathbf{A}_1 & I_1 & S_1 & 1 & 1 & V_{11} & V_{21}\\
\hline
2 & \mathbf{A}_2 & I_2 & S_2 & 2 & 1  & V_{12}  & V_{22}\\
3 & \mathbf{A}_3 & I_3 & S_3 & 2 & 2  & V_{13}  & V_{23}\\
\vdots & \vdots &\vdots &\vdots  &\vdots & \vdots &\vdots  &\vdots\\
\vdots & \vdots & \vdots &\vdots & 2 & l_2 & \vdots  & \vdots\\
\hline
\vdots &\vdots & \vdots &\vdots & 2  & 1& \vdots & \vdots\\
\vdots &\vdots &\vdots &\vdots & 2 & 2& \vdots &  \vdots\\
\vdots &\vdots &\vdots &\vdots &\vdots & \vdots & \vdots  &\vdots \\
\vdots &\vdots &\vdots &\vdots & 2 & k_2 &\vdots  & \vdots\\
\hline
\vdots &\vdots &\vdots &\vdots &\vdots & \vdots &\vdots &\vdots \\
\hline
\vdots & \vdots & \vdots &\vdots  & J &  1 & \vdots & \vdots \\
\vdots &\vdots &\vdots &\vdots &\vdots & \vdots &\vdots &\vdots \\
T & \mathbf{A}_T & I_T &S_T  & J &  l_{J} & V_{1T}& V_{2T}\\
\hline
\vdots &\vdots & \vdots &\vdots & J  & 1& \vdots & \vdots\\
\vdots &\vdots &\vdots &\vdots &\vdots & \vdots & \vdots  &\vdots \\
\vdots &\vdots &\vdots &\vdots & J & k_J &\vdots  & \vdots\\
\hline
\vdots& \vdots & \vdots & \vdots & J+1 & 1 & \vdots& \vdots\\
\vdots &\vdots &\vdots &\vdots &\vdots & \vdots &\vdots &\vdots \\
T^\prime & \mathbf{A}_{T^\prime} & I_{T^\prime} &S_{T^\prime}  & J+1 &  l_{J+1} & V_{1T^\prime}& V_{2T^\prime}\\
\end{array}
\right]
= 
\left[
\begin{array}{c}
\text{column name} \\
\hline
\text{search (start basis)} \\
\hline
\text{search} \\
\text{search} \\
\vdots \\
\text{search (outputted basis)} \\
\hline
\text{interpolate} \\
\text{interpolate} \\
\vdots \\
\text{interpolate} \\
\hline
\vdots \\
\hline
\text{search} \\
\vdots \\
\text{search (final basis)} \\
\hline
\text{interpolate} \\
\vdots \\
\text{interpolate} \\
\hline
\text{search (no output)} \\
\vdots \\
\text{search (no output)} \\
\end{array}
\right]
\label{eq:data-structure}
\end{equation}
